jk test with big K, balanced label

### 2016-10-04 Rmd/convergenceRatesBalancedLabels.Rmd
update

@@

functions to compute misclassification error and rmse of mean estimate:
NB: GMM can get stuck in saddle point at (w1=0, w2=1), so I removed the test result when it happened.
```{r}
computeMError<- function(jk, n,batchN){
  error<- numeric(batchN)
  for(b in 1:batchN){
    newOrder<- order(jk$mu[,1,b],decreasing = T)
    tM0<- c(0,1)[newOrder]
    trueM<- c(rep(tM0[1],(n)),rep(tM0[2],(n)))
    error[b]<- sum (jk$M[,b] != trueM) /2/n
    if( min(jk$w[,b])<0.1){
        error[b]<- NA
    }
  }
  error
}

computeRMSE<- function(jk, mu0, batchN){
  rmse<- numeric(batchN)
  for(b in 1:batchN){
    newOrder<- order(jk$mu[,1,b],decreasing = T)

>>>>

---
title: "jk test with balanced label"
author: "Author"
date: '`r Sys.Date()`'
output:
  md_document: 
    variant: markdown_github
---

@@

functions to compute misclassification error and rmse of mean estimate:
NB: GMM can get stuck in saddle point at (w1=0, w2=1), so I removed the test result when it happened.
```{r}
computeMError<- function(jk, n,batchN){
  error<- numeric(batchN)
  for(b in 1:batchN){
    tM0<- rank(jk$mu[,1,b])-1
    trueM<- rep(tM0,each=n)
    error[b]<- sum ( jk$M[,b] != trueM) /K/n
    if( min(jk$w[,b])<0.1){
        error[b]<- NA
    }
  }
  error
}

computeRMSE<- function(jk, mu0, batchN){
  rmse<- numeric(batchN)
  for(b in 1:batchN){
    newOrder<- order(jk$mu[,1,b],decreasing = F)

### 2016-10-04 Rmd/convergenceRatesBigK.Rmd
update

---
title: "jk test with balanced label"
author: "Author"
date: '`r Sys.Date()`'
output:
  md_document: 
    variant: markdown_github
---

@@

###1. Generate Data
Let's generate data from 2 clusters, with size n, n

N( c(0.7), diag(1.7661/30))
N( c(0.3), diag(1.7661/30))

```{r}
n<- 100
K<- 2
p<- 1
batchN<- 1000

@@

mu0<- c(c(0.7), c(0.3))
mu<- matrix( 0,n*2,p)
mu[1:(n),]<- rep(c(0.7),each=(n))
mu[(n+1):(2*n),]<- rep(c(0.3),each=(n))

sigma<-  sqrt(1.7661/30)

for(b in 1:batchN){
  yBatch[,,b]<- matrix( rnorm(n*p*2,mu,sigma), n*K, p)
}

@@

  K<- 2
  p<- 1
  batchN<- 1000

  mu0<- c(c(0.7), c(0.3))
  mu<- matrix( 0,n*2,p)
  mu[1:(n),]<- rep(c(0.7),each=(n))
  mu[(n+1):(2*n),]<- rep(c(0.3),each=(n))

  sigma<-  sqrt(1.7661/30)

  for(b in 1:batchN){
    yBatch[,,b]<- matrix( rnorm(n*p*2,mu,sigma), n*K, p)
  }

@@

  jk12 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T)
  jk22 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T)
  jGMM12 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F)
  jGMM22 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F)

>>>>

---
title: "jk test with big K, balanced label"
author: "Author"
date: '`r Sys.Date()`'
output:
  md_document: 
    variant: markdown_github
---

@@

###1. Generate Data
Let's generate data:

```{r}
n<- 100
K<- 10
p<- 1
batchN<- 1000

@@

mu0<- c(1:K)
mu<- matrix( 0,n*K,p)
mu <- rep(mu0, each = n)
sigma<-  0.5

for(b in 1:batchN){
  yBatch[,,b]<- matrix( rnorm(n*p*K,mu,sigma), n*K, p)
}

@@

  p<- 1
  batchN<- 1000

  yBatch<- array(0,dim = c(n*K,p,batchN))
  K<- 10

  mu0<- c(1:K)
  mu<- matrix( 0,n*K,p)
  mu <- rep(mu0, each = n)
  sigma<-  0.5

  for(b in 1:batchN){
    yBatch[,,b]<- matrix( rnorm(n*p*K,mu,sigma), n*K, p)
  }

@@

  jk12 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T)
  jk22 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = K,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T)
  jGMM12 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F)
  jGMM22 <- jkmeans::jkmeansEMBatch(yBatch, k=K, j = K,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F)
